A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-06-04 main.tex
Applications of dependent types.

One can use depent types in programming languages such as Idris\cite{brady2013idris} or
interactive theorem provers such as Coq\cite{09thecoq} which based on \cite{coquand:inria-00076024}.
\red{この段落要らないかも}

Applications of dependent types for real problems were also

>>>>

One can use depent types in programming languages such as Idris\cite{brady2013idris} or
interactive theorem provers such as Coq\cite{09thecoq} which based on \cite{coquand:inria-00076024}.
\red{この段落要らない or 後ろとくっつけたほうが良いかも知れない?}

Applications of dependent types for real problems were also researched.
In Xi and Pfenning\cite{Xi98}, they extended SML with restricted dependent types
and succeeded in reducing boundary checking of arrays.
Xi also gave dead code elimination and loop unrolling as examples of dependent types application in \cite{xi1999dependent}.
